# Runnable examples for hierarchical models

```{r setup, include=FALSE}
#knitr::opts_knit$set(root.dir = "exercises")
knitr::opts_chunk$set(message = FALSE)
```


This file will train all four implemented models on a toy data set and shows their results. In case you do not want to train the models (this can take a few hours), you can set the parameter `run==F`, this will only load and print the results. `run==TRUE` will train each of the four models and save/print the results.
Note that since the "training data" here is only the dictionary provided by Statistics Austria, the performance is fairly decreased when compared to "real" training data.
```{r param run}
run <- F
```

First we set up the data. For this, we download the NACE dictionary from the Statistics Austria classification data base: https://www.statistik.at/KDBWeb/kdb_VersionAuswahl.do.
This data is split into training, validation, and test data.
```{r data, message=FALSE}
# load helper functions
source("R/helpers.R")
# load NACE dictionary as toy data set
source("R/load_data_NACE.R")

if(run){
  # load function(s) for hierarchical evaluation
  source("R/eval.R")
  # model definitions
  source("R/helper_transformer.R")
  
  # define target variable to classify
  target <- "Code"
  
  # clean data and split into train/test/valid set
  source("R/train_test_dat.R") 
}
# head training data
head(dat[,.(NACE25,Text)])
```

## Flat Model
The flat model is a global classifier, that ignores the hierarchical structure of the classification codes.
```{r flat}
# Flat Model --------------------------------------------------------------
if(run){
  source("R/flat_model.R")
}else{
  result_flat <- openxlsx::read.xlsx("results/flat_class.xlsx")
}

result_flat
```

## Stacked Model
The stacked model trains one model per hierarchy level, where each subsequent model uses both the original input and the predicted class probabilities from the previous level. To avoid invalid label combinations, predictions are restricted to valid codes by filtering out inconsistent combinations across levels.
```{r stacked}
# Stacked Model -----------------------------------------------------------
if(run){
  source("R/stacked_model.R")
}else{
  res_stacked <- openxlsx::read.xlsx("results/stacked_class.xlsx")
}
res_stacked
```

## Multiple Outputs Model
The multiple output model uses a single model to predict class probabilities for each hierarchy level simultaneously, producing one output vector per level. These outputs must be combined into a valid code.
```{r multipleouts}
# Multiple Outputs Model --------------------------------------------------
if(run){
  source("R/multiple_outputs_model.R")
}else{
  result_multiple_outs <- openxlsx::read.xlsx("results/multiple_outs.xlsx")
}
result_multiple_outs
```

## Hierarchical Loss Model
This model keeps the same input and output as a flat classifier but replaces the standard loss with a combination of cross-entropy and a hierarchical loss that penalizes predictions based on their distance from the true class. By weighting errors according to a penalty matrix, the model is encouraged to prefer predictions that are closer in the hierarchy, with the final loss combining 70% hierarchical loss and 30% cross-entropy.
```{r hierloss}
# Hierarchical Loss -------------------------------------------------------
if(run){
  source("hierarchical_loss_model.R")
}else{
  result_hier_loss <- openxlsx::read.xlsx("results/hierarchical_loss.xlsx")
}
result_hier_loss
```

## Compare all results

```{r results}
rbind(result_flat,
      res_stacked,
      result_multiple_outs,
      result_hier_loss)
```

