# Runnable examples for hierarchical models

```{r setup, include=FALSE}
#knitr::opts_knit$set(root.dir = "exercises")
knitr::opts_chunk$set(message = FALSE)
```


This file will train all four implemented models on a toy data set and shows their results. In case you do not want to train the models (this can take a few hours), you can set the parameter `run==F`, this will only load and print the results. `run==TRUE` will train each of the four models and save/print the results.
Note that since the "training data" here is only the dictionary provided by Statistics Austria, the performance is fairly decreased when compared to "real" training data.
```{r param run}
run <- F
```

First we set up the data. For this, we download the NACE dictionary from the Statistics Austria classification data base: https://www.statistik.at/KDBWeb/kdb_VersionAuswahl.do.
```{r data, message=FALSE}
if(run){
  # load helper functions
  source("R/helpers.R")
  # load NACE dictionary as toy data set
  source("R/load_data_NACE.R")
  # load function(s) for hierarchical evaluation
  source("R/eval.R")
  # model definitions
  source("R/helper_transformer.R")
  
  # define target variable to classify
  target <- "Code"
  
  # clean data and split into train/test/valid set
  source("R/train_test_dat.R") 
}
```


```{r flat}
# Flat Model --------------------------------------------------------------
if(run){
  source("R/flat_model.R")
}else{
  result_flat <- openxlsx::read.xlsx("results/flat_class.xlsx")
}

result_flat
```


```{r stacked}
# Stacked Model -----------------------------------------------------------
if(run){
  source("R/stacked_model.R")
}else{
  res_stacked <- openxlsx::read.xlsx("results/stacked_class.xlsx")
}
res_stacked
```


```{r multipleouts}
# Multiple Outputs Model --------------------------------------------------
if(run){
  source("R/multiple_outputs_model.R")
}else{
  result_multiple_outs <- openxlsx::read.xlsx("results/multiple_outs.xlsx")
}
result_multiple_outs
```


```{r hierloss}
# Hierarchical Loss -------------------------------------------------------
if(run){
  source("hierarchical_loss_model.R")
}else{
  result_hier_loss <- openxlsx::read.xlsx("results/hierarchical_loss.xlsx")
}
result_hier_loss
```

## Compare all results

```{r results}
rbind(result_flat,
      res_stacked,
      result_multiple_outs,
      result_hier_loss)
```

