```{r,setup,echo=FALSE,message=FALSE}
library(ggplot2)
library(data.table)
library(openxlsx)
library(knitr)
```


# Evaluation and Comparison

We evaluate all models using accuracy, top-3 accuracy, top-5 accuracy,
top-10 accuracy, and weighted hierarchical accuracy. The hierarchical
accuracy takes the hierarchy into account, by counting how the number of levels are predicted correctly up to the first incorrect level. If
the first predicted level matches the first true code for the first
level, we count 1/3. If both the first and the second level match, we
count 2/3. If the entire code is predicted, the hierarchical accuracy
will be assigned 1. Note that unless the first level-code is correct, we
always count 0. For a predicted code where the second and third level
are predicted correctly, but the first is not, we will assign 0 to the
prediction. The hierarchical accuracy is then computed by the mean of
assigned values for all outputs codes.

The table below shows the performances of the three hierarchical models
and the flat classifier. The figure displays the same results for easier
comparison. We find that only one of the hierarchical models, the
hierarchical loss model, achieves higher scores than the flat model.
However, this increase in performance is only minimal. The stacked and
the multiple output model rank lower in performance than the flat model.
This could be attributed to the implemented solution of finding the most
probable codes. Altering this process might lead to better predictions.

```{r tab:restable,echo=FALSE,message=FALSE}
flat <- openxlsx::read.xlsx(usethis::proj_path("exercises/results/flat_class.xlsx"))
hloss <- openxlsx::read.xlsx(usethis::proj_path("exercises/results/hierarchical_loss.xlsx"))
stacked <- openxlsx::read.xlsx(usethis::proj_path("exercises/results/stacked_class.xlsx"))
mouts <- openxlsx::read.xlsx(usethis::proj_path("exercises/results/multiple_outs.xlsx"))

res <- do.call(rbind,list(flat,hloss,stacked,mouts))
setDT(res)

res[metric=="accuarcy",metric:="accuracy"]
res_wide <- dcast(res,type ~ metric,  value.var = "value")
names(res_wide) <- c("Model","Accuracy","Hierarchical Accuracy","Top-10 Acc.","Top-3 Acc.","Top-5 Acc.")
res_wide <- res_wide[,.(Model,Accuracy,`Hierarchical Accuracy`,`Top-3 Acc.`,`Top-5 Acc.`,`Top-10 Acc.`)]
res_wide <- res_wide[,c("Accuracy","Hierarchical Accuracy","Top-10 Acc.","Top-3 Acc.","Top-5 Acc."):=round(.SD,4),.SDcols=c("Accuracy","Hierarchical Accuracy","Top-10 Acc.","Top-3 Acc.","Top-5 Acc.")]

knitr::kable(res_wide, caption="Comparison of Model Performances\\label{restable}")
```

```{r,echo=FALSE,message=FALSE,fig.align='center'}
res[,metric:=factor(metric,levels=c("accuracy","hier_accuracy","top3_accuracy","top5_accuracy","top10_accuracy"))]

ggplot(res)+
  geom_bar(aes(x=metric,y=value,fill = type),stat="identity",position="dodge")+
  labs(title="Comparison of model performance",x="",y="")+
  scale_fill_brewer(palette="Set2", name = "Model", 
                    labels = c("Flat","Hierarchical Loss", "Multiple Outputs","Stacked")
                    )+
  scale_x_discrete(labels=c("Accuracy", "hierarchical Acc.", "Top-3 Acc.","Top-5 Acc.","Top-10 Acc."))+
  theme_minimal()
```

The figure below highlights the differences in performance between our implemented
hierarchy-aware models and the flat model.

```{r,echo=FALSE,message=FALSE,fig.align='center'}
diff <- res[, diff_to_flat := value - value[type == "flat"], by = metric]
ggplot(diff[type!="flat",])+
  geom_bar(aes(x=metric,y=diff_to_flat,fill=type),position="dodge",stat="identity")+
  labs(title="Performance differences to flat Model",x="",y="difference")+
  scale_fill_brewer(palette="Set2", name = "Model",
                    labels = c("Hierarchical Loss", "Multiple Outputs","Stacked")
                    )+
  scale_x_discrete(labels=c("Accuracy", "hierarchical Acc.", "Top-3 Acc.","Top-5 Acc.","Top-10 Acc."))+
  geom_hline(yintercept = 0,color="black",linetype="dashed")+
  theme_minimal()
```

